Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-04-03 parts/summary.tex
edits

The way of discovering lenses is changing with the introduction of machine 
learning and citizen science, combined with the coverage of huge areas by 
modern surveys.
The way mass models are generated however remains the same and isn't prepared 
for the increasing influx of lenses to be modelled.
We combine the classical approach, where a small team of experts invest many 
hours into the creation of a single model with the approach of citizen science, 
where a crowd of amateur volunteers make independent contributions.
We recruit motivated citizen scientists, train them to be enthusiast modellers 
and ask them to create early stage models as soon as a lens candidate is 
announced.

To assists the enthusiast modellers assessing their models, we introduce a set 
of diagnostics allowing the qualification of the lenses and the generated 
models and present them alongside the generated models. At a later stage, we 
encourage enthusiast modellers to apply those diagnostics themselves to get a 
preliminary feedback on the plausibility of their models.

@@

The quick creation of many models for the {\SW} candidates successfully showed
that a subset of citizen scientists are interested in being involved in more
challenging tasks that take some time to learn. A next steps involves
recruiting more lensing enthusiasts, as soon as the next round of {\SW} is
started.
In the meantime, the improvements shown in the appendix have to been integrated
into regular {\SpL} usage.
Additionally, photometric fitting could be integrated into {\SpL}.
This would allow the lensing enthusiasts to generate precise photometric
redshifts and thus better stellar masses for all models, without requiring
data from external pipelines.

>>>>

The way of discovering lenses is changing with the introduction of
machine learning and citizen science, combined with the coverage of
huge areas by modern surveys.  The way mass models also needs to
change, in order to be prepared for the increasing influx of lenses to
be modelled.  This work is a hybrid of the classical style, where a
small team of experts invest many hours into the creation of a single
model, with the approach of citizen science, where a crowd of amateur
volunteers make independent contributions.  We are a collaboration of
professionals and experienced citizen-science volunteers, aiming to
create early-stage lens models as soon as a lens candidate is found.

To assists volunteer modellers assessing their models, we introduce a
set of diagnostics allowing the qualification of the lenses and the
generated models and present them alongside the generated models. At a
later stage, we encourage modellers to apply those diagnostics
themselves to get a preliminary feedback on the plausibility of their
models.

@@

The quick creation of many models for the {\SW} candidates successfully showed
that a subset of citizen scientists are interested in being involved in more
challenging tasks that take some time to learn. A next steps involves
recruiting more lensing enthusiasts, as soon as the next round of {\SW} is
started.
In the meantime, the improvements shown in the Appendix have to been integrated
into regular {\SpL} usage.
Additionally, photometric fitting could be integrated into {\SpL}.
This would allow experienced citizen scientists to generate photometric
redshifts and stellar masses, and thus generate preliminary dark-matter maps
as soon as a lens-candidate is identified.
